Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
future work

%\input{inputs/fig_contraction.tex}
%\input{inputs/fig_projection.tex}

@@

An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.

\begin{table}[th]
   \tiny
   \centering
   \caption{Datasets used for evaluation}
   \label{tab:instance_sizes}
   \begin{tabular}{llllc}
      \toprule
         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
      \midrule 
         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
         knott-150        &     572-972         & ???              & 2            & $\times$ \\
         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
         3d-seg           &     101220          & ???              & 1            & $\times$ \\
         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
      \bottomrule
   \end{tabular}
\end{table}

@@

We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.

@@

\begin{table}[th]
   \tiny
   \centering
   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
   \label{tab:eval}
   \begin{tabular}{lllllll}
      \toprule
         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &              &              &  --\\ 
         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &              & $       2.8395$\\
         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &              & $       1.7603$ \\
         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &              & $       6.8908$ \\
         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &              & $       7.1057$\\
         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &              & $       6.5366$ \\
         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &              & $       6.5058$\\   
         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &              & $       4.3319$\\  
         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &              & $\bf    1.3347$ \\  
         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &              & $       2.1347$ \\  
         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &              & $\bf    1.3334$ \\  
         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &              & $       3.3514$ \\      
      \bottomrule
   \end{tabular}
\end{table}

@@

\section{Further Work}\label{sec:future}
So far we have generated the proposals randomly and do not take the current segmentation into account.

So far we only enforce must link constraints to obtain smaller problems.
One can also enforce cannot link constraints to the problem. 
If those are closed, they automatically lead to a decomposition of the problem, 
which is a interesting property for very huge data.

Improving proposals.

>>>>

\input{inputs/fig_contraction.tex}
%\input{inputs/fig_projection.tex}

@@

% An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.

% \begin{table}[th]
%    \tiny
%    \centering
%    \caption{Datasets used for evaluation}
%    \label{tab:instance_sizes}
%    \begin{tabular}{llllc}
%       \toprule
%          Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
%       \midrule 
%          image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
%          knott-150        &     572-972         & ???              & 2            & $\times$ \\
%          knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
%          knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
%          knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
%          3d-seg           &     101220          & ???              & 1            & $\times$ \\
%          socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
%       \bottomrule
%    \end{tabular}
% \end{table}

@@

We use the public available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
For 2D images, we took the segmentation problems on the Berkeley Segmentation Database~\cite{martin_2001} called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
For 3D volume segmentation we took the models \emph{knott-3d-150},\emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underling cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
We also request larger instances from the authors of~\cite{kroeger_2012_eccv} which kindly provide us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
%More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.

@@

\begin{table}[t]
   \tiny
   \centering
   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
   \label{tab:eval}
   \begin{tabular}{lllllll}
      \toprule
         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &              &              &  --\\ 
         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &              & $       2.8395$\\
         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &              & $       1.7603$ \\
         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &              & $       6.8908$ \\
         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &              & $       7.1057$\\
         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &              & $       6.5366$ \\
         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &              & $       6.5058$\\   
         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &              & $       4.3319$\\  
         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &              & $\bf    1.3347$ \\  
         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &              & $       2.1347$ \\  
         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &              & $\bf    1.3334$ \\  
         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &              & $       3.3514$ \\      
      \bottomrule
   \end{tabular}
\end{table}

@@

\section{Future Work}\label{sec:future}
In future work we would like to investigate in much larger problem instances.
Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
If those build a closed surface, the problem decompose into two independent problems.
This is also useful for interactive correlation clustering, by enforcing
updates only in local regions by appropriate proposals.
Overall, a more specific selection of proposals, maybe conditioned on the current solution,
should lead better proposals and to faster progress of CCFusion.
